---
title: "Tutorial 2"
author: "Kugan Parthiban"
date: "2023-11-30"
output: html_document
---

Import Libraries

```{r}
library(dplyr)
library (DataExplorer)
library(VIM)
library(mice)
library(missForest)
library(tidyr)
library(tidyverse)

```

#Load Data

```{r}
df <- read.csv("C:/Users/kugan/Desktop/APU DS/AML/raw data.csv", header = T)



```

#View first 10 rows
```{r}
head(df, n=10)

df$customer_id <- NULL
```
Check for missing values

```{r}

colSums(sapply(df,is.na))

```

Impute 5% of missing values in random with missForest library
```{r}

df_na <- prodNA(df, noNA = 0.05) # introduces 5% missing values at random


#df$country <- prodNA(df$country, noNA = 0.05)
#df$gender <- prodNA(df$gender, noNA = 0.05)
#df$age <- prodNA(df$age, noNA = 0.05)
#df$estimated_salary <- prodNA(df$estimated_salary, noNA = 0.05)
str(df)

```


#Check for missing values 
```{r}

colSums(sapply(df_na,is.na))

```

```{r}
plot_missing (df_na) # uses DataExplorer package

```
#Pareto chart using dlookr package to view the proportion of missing values in each column
```{r}
library(dlookr)
plot_na_pareto(df_na, only_na = T)

```
#Plot to visualize missing values
```{r}
library(VIM)
vim_plot <- aggr(df_na, numbers=TRUE, prop = c(TRUE, FALSE)) # needs 
# Reference and explain this plot
md.pattern(df) # uses mice package

```



```{r}
df_na <- rename(df_na,Country=country,CreditScore=credit_score, Gender=gender, Age=age, Tenure=tenure, BalanceInBank=balance, NumberOfProducts=products_number, CreditCardStatus=credit_card, MembershipStatus=active_member, SalaryEstimate=estimated_salary, ChurnStatus=churn )

df_na
```

```{r}

```


Convert NumberofProducts, country and gender to factors
```{r}
df_na$NumberOfProducts <- as.factor(df_na$NumberOfProducts)
df_na$Country <- as.factor(df_na$Country)
df_na$Gender <- as.factor(df_na$Gender)
df_na$ChurnStatus <- as.factor(df_na$ChurnStatus)
df_na$CreditCardStatus <- as.factor(df_na$CreditCardStatus)
df_na$MembershipStatus <- as.factor(df_na$MembershipStatus)

```

```{r}
summary(df_na)

str(df_na)
```

Impute df_na with mice using linear regression for numerical varaible and random forest for factors
https://www.youtube.com/watch?v=sNNoTd7xI-4&t=1331s

```{r}
#methods(mice)

my_imp <- mice(df_na, m=5,method = c("norm.predict","rf","rf","norm.predict","norm.predict","norm.predict","rf","rf","rf","norm.predict","rf"), maxit=20)



```


Comparing estimated values with the mean values of the numerical features. The imputations have 5 different data frame. Choose the data which estimated values are near to the mean.
```{r}
summary(df_na$Age)
summary(df_na$CreditScore)
summary(df_na$SalaryEstimate)

```
```{r}
my_imp$imp$Age

my_imp$imp$CreditScore

my_imp$imp$SalaryEstimate


```


The 5th dataset is chosen since the estimated values have a smaller deviation to the mean value.

```{r}
final_clean_ds <- complete(my_imp,5)
head(final_clean_ds)

```
#EDA
```{r}
#summary of the data
summary(final_clean_ds)


#data structure
str(final_clean_ds)


#dimension of data
dim(final_clean_ds)

```

```{r}
final_clean_ds$ChurnStatus <- as.factor(final_clean_ds$ChurnStatus)
final_clean_ds$CreditCardStatus <- as.factor(final_clean_ds$CreditCardStatus)
final_clean_ds$MembershipStatus <- as.factor(final_clean_ds$MembershipStatus)

summary(final_clean_ds)
str(final_clean_ds)
```




```{r}

#https://www.youtube.com/watch?v=McL9MMwmIZY
head(final_clean_ds)

library(ggplot2)

#scatter plot between 2 continous variable

ggplot(final_clean_ds,aes(x=Age,y=BalanceInBank)) +
  geom_point(color='red') +
  labs(x="Age",
       y="Balance in Bank",
       title="Age vs Balance in Bank")

#Histogram
ggplot(final_clean_ds,aes(x=Age)) +
  geom_histogram(bins=20)


#frequency polygon
#Histogram
ggplot(final_clean_ds,aes(x=Age)) +
  geom_freqpoly(bins=10)

#Bar chart (Target Variable)
ggplot(final_clean_ds, aes(x=ChurnStatus)) +
  geom_bar(color='black',
           fill="skyblue")

ggplot(final_clean_ds, aes(x=ChurnStatus,
              fill=ChurnStatus)) +
  geom_bar() +
  scale_fill_brewer(palette = 'Dark2')

#boxplot 
ggplot(final_clean_ds, aes(x=ChurnStatus,
                           y=BalanceInBank,
                           fill=ChurnStatus)) +
  geom_boxplot(show.legend=FALSE)  +
  scale_fill_brewer(palette = 'Dark2')


#bar chart to displace number of products prchased by the customer
plot_bar(final_clean_ds$NumberOfProducts)

#Gender
plot_bar(final_clean_ds$Gender, title = 'Gender')

#Country
barplot(table(final_clean_ds$Country), main="Country Distribution", col = c('orange','skyblue', 'grey'))




```

#Checking unique values for categorical column for label encoding
```{r}
unique(final_clean_ds$Country)

unique(final_clean_ds$Gender)


```
#label encoding 
```{r}
final_clean_ds$Gender <- factor(final_clean_ds$Gender, 
                                levels = c("Female", "Male"),
                                labels = c(0,1))

View(final_clean_ds)

```

#one hot encoding
```{r}
encoded1_df <- final_clean_ds %>%
  mutate(France = ifelse(final_clean_ds$Country == "France",1,0),
         Germany = ifelse(final_clean_ds$Country == "Germany", 1,0),
         Spain = ifelse(final_clean_ds$Country == "Spain", 1,0))

View(encoded1_df)



```


#standardization
#https://www.youtube.com/watch?v=ewpVWnEapoA
```{r}
#numerical column is normalized with z-score with mean=0 and SD=1

z_score <- function(x){
  res <- (x-mean(x))/sd(x)
  return(res)
}

encoded1_df[,c(1,4,5,6,10)] <- sapply(encoded1_df[,c(1,4,5,6,10)], z_score)
View(encoded1_df)

```

#Drop country column
```{r}

encoded1_df$Country <- NULL
View(encoded1_df)

```